---
title: "Data Analysis Project"
author: "D. Bracy , H.H. Nguyen, S.Purvis"
date: "3/11/2020"
output:
  word_document: 
    reference_docx: "wordStyleRef.docx"
  html_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(MASS)



# wordStyleRef style changes:
## Set margins to .5"
## Heading 1 creates page break before line
## Heading 2 remove space before
## Heading 5 centers text (#####) 

```


## R Markdown

Suggested Downtime Activities:  

1. Data cleaning (handle missing?,  train/test split logistics:  you want a good balance of Y/N in your train)
2. summary statistics (the ones I kept complaining about on Project 1)
3. EDA (basic boxplots, scatterplots, bar charts etc to see how things relate to the response, PCA tool),
4. Maybe play around and fit a few LDA models with continuous stuff.

##### ![caption](https://whitelabel.2u.com/cdn/v1/smu-mds/compass-dark.svg){width=10%}


Note this is just a syntax example. Since we don't have a local picture to use, this will show nothing in the word doc.  Also worth noting is the H5 marking, which centers the image.


#### Latex examples:

$$Variance Ratio=  \frac{(σ_{max})^2}{(σ_{min} )^2} = \frac{2.84^2}{1.20^2} =5.6$$

$$log(ReportDeliveryTime) = SchedFreq + HourOfDay + DayOfMonth + ReportCategory + Server$$



```{r read data}
#reading in 'Bank Additional' file
bank = read.csv("./DataSets/bank-additional.csv",header = TRUE, sep = ";")
str(bank)
summary(bank)
sum(is.na(bank))

#reading in 'Bank Additional Full' file
bankfull = read.csv("./DataSets/bank-additional-full.csv",header = TRUE, sep = ";")
str(bankfull)
summary(bankfull)
sum(is.na(bankfull))
```


```{r Feature Engineering}



```



```{r EDA}


df <- bank # input dataframes for plots

df %>% ggplot(aes(y, age)) + geom_boxplot() + coord_flip()
df %>% ggplot(aes(job, y, fill=y)) + geom_col()
df %>% ggplot(aes(marital, y, fill=y)) + geom_col()
df %>% ggplot(aes(education, y,  fill=y)) + geom_col()
df %>% ggplot(aes(default, y,  fill=y)) + geom_col()
df %>% ggplot(aes(housing, y,  fill=y)) + geom_col()
df %>% ggplot(aes(loan, y,  fill=y)) + geom_col()
df %>% ggplot(aes(contact, y,  fill=y)) + geom_col()
df %>% ggplot(aes(month, y,  fill=y)) + geom_col()
df %>% ggplot(aes(day_of_week, y,  fill=y)) + geom_col()
df %>% ggplot(aes(y, duration)) + geom_boxplot() + coord_flip()
df %>% ggplot(aes(campaign, y,  fill=y)) + geom_col()
df %>% ggplot(aes(y, campaign)) + geom_boxplot() + coord_flip()

df %>% ggplot(aes(pdays, y,  fill=y)) + geom_point()

df %>% ggplot(aes(previous, y,  fill=y)) + geom_col()
df %>% ggplot(aes(poutcome, y,  fill=y)) + geom_col()


df %>% ggplot(aes(emp.var.rate, y,  fill=y)) + geom_col()
df %>% ggplot(aes(y, emp.var.rate)) + geom_boxplot() + coord_flip()

df %>% ggplot(aes(cons.price.idx, y,  fill=y)) + geom_col()
df %>% ggplot(aes(y, cons.price.idx)) + geom_boxplot() + coord_flip()


df %>% ggplot(aes(cons.conf.idx, y,  fill=y)) + geom_col()
df %>% ggplot(aes(y, cons.conf.idx)) + geom_boxplot() + coord_flip()


df %>% ggplot(aes(euribor3m, y,  fill=y)) + geom_col()
df %>% ggplot(aes(y, nr.employed)) + geom_boxplot() + coord_flip()

df %>% ggplot(aes(nr.employed, y,  fill=y)) + geom_col()
df %>% ggplot(aes(y, nr.employed)) + geom_boxplot() + coord_flip()

```





```{r LDA analysis}

# Select only continuous variables:
bankCont <- dplyr::select(bankfull, c('age','duration', 'campaign', 'pdays', 'cons.price.idx', 'cons.conf.idx', 'euribor3m', 'nr.employed','y'))
bankCont$age <- as.numeric(bankCont$age)
bankCont$duration <- as.numeric(bankCont$duration)
bankCont$campaign <- as.numeric(bankCont$campaign)
bankCont$pdays <- as.numeric(bankCont$pdays)


mylda<-lda(y~age+duration+ campaign+ pdays+ cons.price.idx+ cons.conf.idx+ euribor3m+ nr.employed, data=bankCont)
pred<-predict(mylda,newdata=bankCont)$class  #Predictions can come in many forms, the class form provides the categorical level of your response.
Truth<-bankCont$y
x<-table(pred,Truth) # Creating a confusion matrix
x
#Missclassification Error
ME<-(x[2,1]+x[1,2])/1000
ME

```


```{r PCA Analysis}

pc.bankCont<-prcomp(bankCont[,-9],scale.=TRUE)
pc.bankCont.scores<-pc.bankCont$x

#Adding the response column to the PC's data frame
pc.bankCont.scores<-data.frame(pc.bankCont.scores)
pc.bankCont.scores$y<-bankCont$y

pc.bankCont.scores

#Use ggplot2 to plot the first few pc's
ggplot(data = pc.bankCont.scores, aes(x = PC1, y = PC2)) +
  geom_point(aes(col=y), size=1)+
  ggtitle("PCA of Subscriptions")

ggplot(data = pc.bankCont.scores, aes(x = PC2, y = PC3)) +
  geom_point(aes(col=y), size=1)+
  ggtitle("PCA of Subscriptions")


```

```{r}
library(caret) 
library(e1071)
library(rpart)
library(rpart.plot)
library(rattle)
library(randomForest)
library(caTools)
library(descr)
#########################################################
# Sampling the dataset into training data and test data:
#############################################################

set.seed(1234)
splitPerc = .75
index = sample(1:dim(bankCont)[1],round(splitPerc * dim(bankCont)[1]))
#index<-sample(1:dim(Auto2)[1],192,replace=F)
traindata<-bankCont[index,]
testdata<-bankCont[-index,]

  


# Classification and Regression Trees
bank.cart<-rpart(y ~ ., traindata , method = 'class')

#par(mfrow=c(1,1))
#fancyRpartPlot(bank.cart , digits=2 , palettes = c("Purples", "Oranges"))

#predict
cart_pred <- predict( bank.cart , testdata , type = "class")
cart_prob <- predict( bank.cart , testdata , type = "prob")

# Confusion matrix
confusionMatrix(cart_pred , testdata$y)

### Cross table validation for CART
CrossTable(testdata$y, cart_pred,
          prop.chisq = FALSE, prop.c = FALSE, prop.r = FALSE,
          dnn = c('actual default', 'predicted default'))
```



```{r knn}
#Implementing KNN
###########################################
bank.knn <- train(y ~ ., data = traindata, method = "knn", 
                  maximize = TRUE,
                  trControl = trainControl(method = "cv", number = 10),
                  preProcess=c("center", "scale"))

predictedkNN <- predict(bank.knn , newdata = testdata)
confusionMatrix(predictedkNN , testdata$y)

### Cross table validation for KNN
CrossTable(testdata$y, predictedkNN,
           prop.chisq = FALSE, prop.c = FALSE, prop.r = FALSE,
           dnn = c('actual default', 'predicted default'))
```






